This is an example of article title

### 2025-04-11 paper/paper.tex
final touches

To ensure the required surface finish, the machined features must enclose the pre-cast features on the blank (called rough features) with a minimum machining allowance (a lower bound parameter).
The allowance calculation requires the final part specification in the form of the machining CNC code as well as a representation of the rough geometries.
From their positions and geometric parameters their distance can be computed, which then can be used to generate the allowance constraints for the optimization program.

@@

Future plans for the package and the method itself include an overhaul of the tolerance modelling scheme.
It should be possible to generalize the current dimensional tolerances for  more GD\&T tolerances by introducing a new type hierarchy based on the current geometry type tree and a function interface for the optimization program.
Another direction of development is to extend the supported operations from drilling and milling to others, such as turning, although this is more a research question than an implementation.

>>>>

To ensure the required surface finish, the machined features must enclose the pre-cast features (rough features) on the blank with a minimum machining allowance (a lower bound parameter).
The allowance calculation requires the final part specification in the form of the machining CNC code as well as a representation of the rough geometries.
From their positions and geometric parameters their distance can be computed, which then can be used to generate the allowance constraints for the optimization program.

@@

Future plans for the package and the method itself include an overhaul of the tolerance modelling scheme.
It should be possible to generalize the current dimensional tolerances for  more GD\&T tolerances by introducing a new type hierarchy based on the current geometry type tree and a function interface for the optimization program.
Another direction of development is to extend the supported operations from drilling and milling to others, such as turning, although this is more of a research question than an implementation issue.
